---
title: "Google stocks"
author: "Megha Roy"
date: "21/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing Libraries
```{r}
library(ggplot2)
library(tseries)
library(forecast)
library(reshape2) 
library(astsa)
```

The AirPassenger dataset in R provides monthly totals of a US airline passengers, from 1949 to 1960. 





```{r}
data(AirPassengers)
AirPassengers
```

### Checking for missing values
```{r}
sum(is.na(AirPassengers))
```
```{r}
boxplot(AirPassengers)
```

There are no missing values and outliers in the data. 


```{r}
start(AirPassengers)
```


```{r}
 end(AirPassengers)
```
```{r}
summary(AirPassengers)
```

### Cyclic Variation 
```{r}
plot(AirPassengers)

```

The passenger numbers increase over time with each year.As an inference, over an year the no. of passengers increase particularly during July to September and decrease after it.


```{r}
cycle(AirPassengers)

```

### TREND 
```{r}
plot(aggregate(AirPassengers,FUN=mean))
```



```{r}
boxplot(AirPassengers~cycle(AirPassengers))

```

In the boxplot there are more passengers traveling in months 6 to 9 with higher means and higher variances than the other months, indicating seasonality with a apparent cycle of 12 months.
```{r}

```






```{r}
trends<-decompose(AirPassengers, "multiplicative")
plot(trends)
```



### Check whether data is stationary or not

AUGMENTED DICKEY FULLER TEST
```{r}
adf.test(AirPassengers, alternative = "stationary")
```
As a rule of thumb, where the p-value is less than 5%, we strong evidence against the null hypothesis, so we reject the null hypothesis. As per the test results above, the p-value is 0.01 which is <0.05 therefore we reject the null in favour of the alternative hypothesis that the time series is stationary.



```
```{r}

```

```

```

```



